**Results Template**

### 2021-10-07 1_descriptive.Rmd
descriptive and interaction models
condition*instruction
style*instruction

```{r}
ggplot(df, aes(yoni_total)) + geom_histogram()
ggplot(df, aes(BES_total)) + geom_histogram()
ggplot(df, aes(yoni_total, BES_total)) + geom_point()
ggplot(df, aes(HCT_accuracy)) + geom_histogram()
ggplot(df, aes(MAIA_total)) + geom_histogram()
ggplot(df, aes(HCT_accuracy, MAIA_total)) + geom_point()
```

>>>>

```{r}
df.plot <- df %>% 
  group_by(ID, condition, instruction) %>% 
  summarise(confidence = mean(DT_confidence, na.rm = TRUE),
            RT = mean(DT_RT, na.rm = TRUE),
            yoni_total = mean(yoni_total, na.rm = TRUE),
            BES_total = mean(BES_total, na.rm = TRUE),
            HCT_accuracy = mean(HCT_accuracy, na.rm = TRUE),
            MAIA_total = mean(MAIA_total, na.rm = TRUE))
```

```{r independent var}
ggplot(df.plot, aes(yoni_total)) + geom_histogram()
ggplot(df.plot, aes(BES_total)) + geom_histogram()
ggplot(df.plot, aes(yoni_total, BES_total)) + geom_point()
ggplot(df.plot, aes(HCT_accuracy)) + geom_histogram()
ggplot(df.plot, aes(MAIA_total)) + geom_histogram()
ggplot(df.plot, aes(HCT_accuracy, MAIA_total)) + geom_point()
```

```{r dependent var}
ggplot(df, aes(DT_confidence)) + geom_density()
ggplot(df, aes(DT_RT)) + geom_density()

ggplot(df, aes(instruction, DT_confidence)) + geom_boxplot()
# much higher confidence in truth
ggplot(df, aes(instruction, DT_RT)) + geom_boxplot()
# no diff in reaction time in truth or lie

ggplot(df, aes(condition, DT_confidence)) + geom_boxplot()
ggplot(df, aes(condition, DT_RT)) + geom_boxplot()
# not much diff for diff conditions

ggplot(df, aes(DT_RT, DT_confidence)) + geom_point()
# RT and confidence don't seem to have a correlation
```

```{r both}
# is there a way to loop this
ggplot(df.plot, aes(x = yoni_total, y = confidence, colour = instruction)) +
  geom_point() +
  geom_smooth(method = "lm") + 
  facet_wrap(~condition)

ggplot(df.plot, aes(x = BES_total, y = confidence, colour = instruction)) +
  geom_point() +
  geom_smooth(method = "lm") + 
  facet_wrap(~condition)
# both yoni and BES do not seem to have effect in social condition, higher yoni/BES increases confidence in truth and decreases confidences in lie

ggplot(df.plot, aes(x = HCT_accuracy, y = confidence, colour = instruction)) +
  geom_point() +
  geom_smooth(method = "lm") + 
  facet_wrap(~condition)
# same effect in both social and polygraph, higher HCT accuracy decreases confidence in truth and increases confidence in lie

ggplot(df.plot, aes(x = MAIA_total, y = confidence, colour = instruction)) +
  geom_point() +
  geom_smooth(method = "lm") + 
  facet_wrap(~condition)
# same effect for lie in both social and polygraph, higher MAIA increases confidence
# higher MAIA increases confidence in lie for social and not polygraph

# interesting that the social tests are more correlated with polygraph and vice versa
```

### 2021-10-07 2_inferential.Rmd
descriptive and interaction models
condition*instruction
style*instruction

```{r}
y.var <- c('DT_confidence', 'DT_confidence', 'DT_confidenceRT')
x.var <- c('DT_confidenceRT', 'condition*instruction', 'condition*instruction')

for (i in seq_along(y.var)){
  for (j in seq_along(x.var)){
    if (i==j){
      model <- lmer(paste(y.var[i],' ~', x.var[j],' + (1|ID) + (1|item) + (1|trial)'), df)
      print(report(model))
      print(parameters(model, effects = "fixed"))
      if (grepl('\\*', x.var[j]) == TRUE){
        p <- interactions::cat_plot(model, pred = instruction, modx = condition)
      }
      else{
        viz_data <- estimate_relation(model)
        p <- ggplot(data = viz_data, aes(x = DT_confidenceRT, y = Predicted)) +
          geom_line() +
          geom_ribbon(aes(ymin = CI_low, ymax = CI_high), alpha = 0.3) +
          geom_point(data = df, aes(x = DT_confidenceRT, y = DT_confidence, color = ID))
      }
      print(p)
    }
  }
}
```

```{r}
model <- lmer(DT_confidence ~ DT_confidenceRT + (1|ID) + (1|item) + (1|trial), df)
report(model)
parameters(model, effects = "fixed")
viz_data <- estimate_relation(model)
p <- ggplot(data = viz_data, aes(x = DT_confidenceRT, y = Predicted)) +
  geom_line() +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high), alpha = 0.3) +
  geom_point(data = df, aes(x = DT_confidenceRT, y = DT_confidence, color = ID))
p
#R2 does not account for random effects
#weirdly significant given the plot
#what's the include_random thing (6.5 vs 6.7)
```

```{r}
model <- lmer(DT_confidence ~ condition*instruction + (1|ID) + (1|item) + (1|trial), df)
report(model)
parameters(model, effects = "fixed")
interactions::cat_plot(model, pred = instruction, modx = condition)
#R2 does not account for random effects
#interaction is significant
```

```{r}
model <- lmer(DT_confidenceRT ~ condition*instruction + (1|ID) + (1|item) + (1|trial), df)
#actually this is not the reaction time? it's the reaction time to the question of how confident
```

>>>>

```{r loop archive}
y.var <- c('DT_confidence', 'DT_confidence', 'DT_RT')
x.var <- c('DT_RT', 'condition*instruction', 'condition*instruction')

for (i in seq_along(y.var)){
  for (j in seq_along(x.var)){
    if (i==j){
      model <- lmer(paste(y.var[i],' ~', x.var[j],' + (1|ID) + (1|item) + (1|trial)'), df)
      print(report(model))
      print(parameters(model, effects = "fixed"))
      if (grepl('\\*', x.var[j]) == TRUE){
        p <- interactions::cat_plot(model, pred = instruction, modx = condition)
      }
      else{
        viz_data <- estimate_relation(model)
        p <- ggplot(data = viz_data, aes(x = DT_RT, y = Predicted)) +
          geom_line() +
          geom_ribbon(aes(ymin = CI_low, ymax = CI_high), alpha = 0.3) +
          geom_point(data = df, aes(x = DT_RT, y = DT_confidence, color = ID))
      }
      print(p)
    }
  }
}
```

```{r confidence and RT}
model <- lmer(DT_confidence ~ DT_RT + (1|ID) + (1|item), df) # removed trial
parameters(model, effects = "fixed")
viz_data <- estimate_relation(model)
p <- ggplot(data = viz_data, aes(x = DT_RT, y = Predicted)) +
  geom_line() +
  geom_ribbon(aes(ymin = CI_low, ymax = CI_high), alpha = 0.3) +
  geom_point(data = df, aes(x = DT_RT, y = DT_confidence, color = ID))
p
# there's still a singular fit?
# weirdly significant given the plot
# what's the include_random thing (6.5 vs 6.7)
```

```{r condition*instruction}
y.var <- c('DT_confidence', 'DT_RT')

for (i in seq_along(y.var)){
  model <- lmer(paste(y.var[i],' ~ condition*instruction + (1|ID) + (1|item)'), df)
  print(parameters(model, effects = "fixed"))
  means <- modelbased::estimate_means(model, at = c("condition", "instruction"))
  contrasts <- modelbased::estimate_contrasts(model, contrast = c("condition", "instruction"))
  p <- ggplot(means, aes(x = instruction, y = Mean, colour = condition)) + 
    geom_line(aes(group = condition)) +
    geom_pointrange(aes(ymin = CI_low, ymax= CI_high))
  print(p)
}
# what's the better way to loop
# significant interaction for confidence: in truth, polygraph increases confidence but no diff in lie
# non-significant interaction for RT
```

```{r style*instruction}
y.var <- c('DT_confidence', 'DT_RT')

for (i in seq_along(y.var)){
  model <- lmer(paste(y.var[i],' ~ style*instruction + (1|ID) + (1|item)'), df)
  print(parameters(model, effects = "fixed"))
  means <- modelbased::estimate_means(model, at = c("style", "instruction"))
  contrasts <- modelbased::estimate_contrasts(model, contrast = c("style", "instruction"))
  p <- ggplot(means, aes(x = instruction, y = Mean, colour = style)) + 
    geom_line(aes(group = style)) +
    geom_pointrange(aes(ymin = CI_low, ymax= CI_high))
  print(p)
}
# non-significant interaction for both (large CI)
```

```{r}
model <- lmer(DT_confidence ~ condition*instruction + (1|ID) + (1|item), df)
report(model)
parameters(model, effects = "fixed")
means <- modelbased::estimate_means(model, at = c("condition", "instruction"))
contrasts <- modelbased::estimate_contrasts(model, contrast = c("condition", "instruction"))
ggplot(means, aes(x = instruction, y = Mean, colour = condition)) + 
  geom_line(aes(group = condition)) +
  geom_pointrange(aes(ymin = CI_low, ymax= CI_high))
performance::performance(model)
```

### 2021-10-07 index.Rmd
descriptive and interaction models
condition*instruction
style*instruction

```{r warning=FALSE, message=TRUE, results='asis'}
library(bayestestR)
library(parameters)
library(performance)
library(report)
library(see)
library(ggplot2)

>>>>

```{r warning=FALSE, message=TRUE, results='asis'}
library(tidyverse)
library(lme4)
library(report)
library(parameters)
library(modelbased)
library(performance)
library(bayestestR)
library(see)
